Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_payment.tex
stating once that proofs are in appendix

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.

@@

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
&\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \nonumber \\
=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) \nonumber  \\
=& O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

>>>>

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments.

@@

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)}}  \\
& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
\; = \; O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}
